%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%  
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
\usepackage{tikzpagenodes}
\usepackage[document]{ragged2e}





\pagestyle{fancy}
\fancyhf{}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Artur}{Podsiadły}{
    \href{mailto:artpods56@gmail.com}{\faEnvelopeO\ artpods56@gmail.com}\hspace{0,25cm} 
    \href{https://www.linkedin.com/in/artpods56/}{\faLinkedin\ linkedin.com/in/artpods56} \\
    \href{https://github.com/artpods56}{\faGithub\ github.com/artpods56} \hspace{0,25cm} 
    \faMobile{ +48 530-670-682} 
}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.4\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROFESSIONAL SUMMARY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{About Me}
\subsection{Machine Learning Engineer}
Bridging the gap between research and robust software engineering.
Specialized in building end-to-end production systems with a focus on scalability, clean code, and MLOps automation in the fields of LLMs and Deep Learning (Computer Vision \& Document AI).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     BEYOND CODE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Beyond Code}
Outside of work, I enjoy thrifting and collecting vintage clothing.
I also play RPG games and practice table tennis regularly.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LANGUAGES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Languages}
Polish (Native) \textbullet{} English (B2+)


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     CERTIFICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Certifications}
%\textbf{Technical certificate EE.09} \\
%
%\textbf{Technical certificate EE.08} \\
%
%\textbf{Cisco Networking Academy - IT Essentials} \\
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%\section{Coursework}
%\subsection{Graduate}
%Fundamentals of Machine Learning \\
%Deep Neural Networks in Data Processing \\
%Natural Language Processing \\
%Deep Neural Networks in Computer Vision

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Development}
Python (SOLID, Clean Code, TDD) \\
PyTorch • RAG systems • Vision LLMs \\
Hugging Face • OpenAI API • LangGraph • Pydantic • Pandas • MCP • OpenRouter
\sectionsep

\subsection{ML Platform \& MLOps}
Dagster • Docker • Label Studio • W\&B \\
MinIO • Redis • Celery • RabbitMQ • llama.cpp
\sectionsep

\subsection{Backend \& APIs}
FastAPI • Django • SQLAlchemy • PostgreSQL • Nginx • Git • Postman

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{\href{https://github.com/artpods56/KUL_OCR}{KUL OCR}}
\descript{OCR microservice}
Scalable OCR service with FastAPI, Celery, and Tesseract featuring asynchronous task processing and Docker deployment.
\sectionsep

\runsubsection{\href{https://github.com/artpods56/KUL_Notarius}{Notarius}}
\descript{Information extraction}
Advanced information extraction system built around Vision LLMs and LayoutLMv3 model architecture.
Features end-to-end data processing pipeline managed by Dagster and experiment tracking powered by W\&B.
\sectionsep

\runsubsection{\href{https://github.com/mereolog/ml-playground}{ML Playground}} \\
\descript{Interactive ML visualization}
Web platform built with Django and Fastapi for real-time ML algorithm experimentation with interactive parameter tuning and visual feedback.
\sectionsep




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.55\textwidth} 

\section{Education}
\subsection{The John Paul II}
\subsection{Catholic University of Lublin}
\descript{Master of Computer Science}
\location{Oct 2025 - Present | In Progress}
\descript{Bachelor of Artificial Intelligence \\ Thesis: "Evolution of RAG (Retrieval-Augmented Generation) systems"}
\location{Oct 2022 - June 2025 | Graduated}
\sectionsep

\subsection{Power Engineering School Complex named after Prof. Kazimierz Drewnowski in Lublin}
\descript{IT Technician Specialization}
\location{2017 | 2021}
\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{The John Paul II Catholic University of Lublin} \\
\descript{Software Engineer / Technical Mentor}
\descript{\href{https://github.com/artpods56/KUL_OCR}{KUL ocr - Github Repository}}
\location{October 2025 - Present | Lublin}
\vspace{\topsep}
\begin{tightemize}
\item Led student internship program, designing a production-ready service that enabled students to work on a real project in a team environment.
\item Managed self-hosted GitLab instance and CI/CD runners, implementing development workflows and code quality standards for team collaboration.
\end{tightemize}
\sectionsep

\runsubsection{Institute for the Historical Geography of the Church in Poland} \\
\descript{ML Engineer (MLOps / LLM Systems)}
\descript{\href{https://github.com/artpods56/KUL_Notarius}{Notarius Project - Github Repository}}
\location{March 2025 - August 2025 | Lublin}
\begin{tightemize}
\item Designed end-to-end information extraction system (Layout Analysis + Vision LLMs) that achieves >90\% accuracy per separate document.
\item Collaborated closely with historians to capture domain-specific document structures and constraints, translating expert knowledge into model and pipeline design.
\item Configured production annotation platform (Docker, Label Studio, MinIO) with MLOps best practices including model versioning and experiment tracking (W\&B).
\end{tightemize}
\sectionsep

\runsubsection{\href{https://tedxlublin.org}{TEDxLublin}} \\
\descript{IT / Web Design and Development }
\descript{\href{https://www.tedxlublin.org}{www.tedxlublin.org - Website}}
\location{March 2024 - Present | Lublin}

\begin{tightemize}
\item Designed and developed the official TEDxLublin website that enabled seamless event management and allowed the organization to focus on delivering a great experience for attendees.
%\item Integrated Umami for privacy-focused web analytics, ensuring GDPR compliance and data security.
\end{tightemize}
\sectionsep
%


\end{minipage}

\vfill
\begin{center}
    \scriptsize
    I authorise the processing of personal data contained within my CV, according to GDPR (EU) 2016/679, Article 6.1(a).
\end{center}

\end{document}
